---
title: "The Farmer Dog"
author: "Amara Diallo"
date: "12/7/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
```


Looking at only the United States, France, and Spain, what was the median revenue in 2013? (Taking the three countries together in aggregate) *

```{r}
`The.Farmer's.Dog` <- read.csv("C:/Users/User/Desktop/The Farmer's Dog.csv")

median_2013 <- `The.Farmer's.Dog` %>%
    select(country, year, revenue) %>%
    filter(country %in% c('US','FR', 'ES'), year =="2013") %>%
    
    #group_by(country, year) %>%
    summarize(median_3_country= median(revenue))

median_2013
```

Was it more or less than 2012? *

```{r}
median_2012 <- `The.Farmer's.Dog` %>%
    select(country, year, revenue) %>%
    filter(country %in% c('US','FR', 'ES'), year =="2012") %>%
    
    #group_by(country, year) %>%
    summarize(median_3_country= median(revenue))

median_2012
```

What drove that difference? *

```{r}
drove_2012 <- `The.Farmer's.Dog` %>%
    select(country, year, revenue,product_group) %>%
    filter(country %in% c('US','FR', 'ES'), year =="2012") %>%
    
    group_by(country,product_group) %>%
    summarize(revenue_m= median(revenue),
              sum_revenue = sum(revenue)) %>%
    mutate(product_group = product_group %>% 
               as_factor() %>% fct_reorder(revenue_m)) %>%
    
    arrange(desc(revenue_m)) %>%
    ungroup()

drove_2012
```

```{r}
# drove_2013 <- `The.Farmer's.Dog` %>%
#     select(country, year, revenue, product_group) %>%
#     filter(country %in% c('US','FR', 'ES'), year =="2013") %>%
#     
#     group_by( country,product_group) %>%
#     summarize(revenue_m= median(revenue),
#               sum_revenue = sum(revenue)) %>%
#     ungroup()
# 
# drove_2013

 
drove_2013 <- `The.Farmer's.Dog` %>%
    select(country, year, revenue,product_group) %>%
    filter(country %in% c('US','FR', 'ES'), year =="2013") %>%
    
    group_by(country,product_group) %>%
    summarize(revenue_m= median(revenue),
              sum_revenue = sum(revenue)) %>%
    mutate(product_group = product_group %>% 
               as_factor() %>% fct_reorder(revenue_m)) %>%
    
    arrange(desc(revenue_m)) %>%
    ungroup()

drove_2013

drove_2013 %>%
    ggplot(aes(product_group, revenue_m, fill = country)) +
    geom_col() +
    scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M")) +
    coord_flip()
```

Looking now at all countries, which product group had the biggest decline in median revenue from 2013 to 2014, by dollar amount? *

```{r}
biggest_decline_prod <- `The.Farmer's.Dog` %>%
    select(country, year, revenue,product_group) %>%
    filter(year %in% c("2013", "2014")) %>%
    
    group_by(year, product_group) %>%
    summarize(revenue_m= median(revenue)) %>%
    
    arrange(desc(product_group)) %>%
    ungroup() 

biggest_decline_prod


```

Looking now at all countries, which product group had the biggest decline in median revenue from 2013 to 2014, by percent change? 

```{r}
# biggest_decline_prod %>%
#     mutate(revenue_m_dif = lag(revenue_m, n =1)) %>%
#     mutate(revenue_m_dif = case_when(
#         is.na(revenue_m_dif) ~ revenue_m,
#         TRUE ~ revenue_m_dif
#     )) %>%
#     
#     mutate(diff_1 = revenue_m - revenue_m_dif) %>%
#     mutate(pct_diff_1 = diff_1/revenue_m_dif) %>%
#     mutate(pct_diff_1_chr = scales::percent(pct_diff_1, accuracy = 3)) %>%
#     
#     select(year, product_group,revenue_m, pct_diff_1_chr) %>%
#     filter(product_group=='clothing') %>%
#     arrange(desc(product_group))


biggest_decline_prod %>%
    group_by(product_group) %>%
    mutate(pct_change = (revenue_m/lag(revenue_m)-1) * 100) %>%
    mutate(pct_change = scales::percent(pct_change,scale = 3)) %>%
    
    filter(product_group=='clothing') 
    
    #arrange(year, .by_group = TRUE)


```


